Home

### 2021-07-02 analysis/index.Rmd
refactor: remove about page

Please find all project details in the [About](about.html) page.

>>>>

# Acknowledgment

This work is part of the [AMPEL](https://ampel.care/en/)
(Analysis and Reporting System for the Improvement of Patient Safety through
Real-Time Integration of Laboratory Findings) project.

This measure is co-funded with tax revenues based on the budget adopted by
the members of the Saxon State Parliament.
